### 2008-10-08 trunk/Papers/rmrs-08/rmrs.tex

One aspect in which our definition of \rmrs\ is like dominance
constraints and unlike \mrs\ is that any satisfiable \rmrs\ has an
infinite number of models which only differ in the areas that the
\rmrs\ didn't ``talk about''.  Consider e.g.\ (\ref{ex:cat-erg}).
Read as an \mrs\ or as an \rmrs\ of the previous literature, this
formula is an instruction to build a semantic representation out of
the pieces for ``every fat cat'', ``some dog'', and ``chased''; a
semantic representation as in Fig.~\ref{fig:fat-black-cat} would
\emph{not} be taken as described by this \rmrs\.  However, under the
semantics we proposed above, this tree is a correct model of
(\ref{ex:cat-erg}) because all atoms are still satisfied; the \rmrs\
didn't say anything about ``sleep'' or ``run'', but it couldn't
enforce that the tree shouldn't contain those subformulas either.

@@

So far we have based the syntax and semantics of \rmrs\ on the
dominance relation from \newcite{egg:etal:2001} rather than the qeq
relation from \newcite{copestake:etal:2005}.  This is partly because
dominance is a weaker relation than qeq: If a dependency parser links
a determiner to a noun and this noun to a verb, then we can use
dominance but not qeq to represent that the predicate introduced by
the verb is outscoped by the quantifier introduced by the determiner
(see earlier discussion).  However, it is very straightforward to add
qeq to the syntax of the language and to extend the model theory
accordingly.  This extension adds a new atom $X=_q Y$ to
Def.~\ref{defn:rmrs-syntax}, and $\tau,\alpha,g,\sigma$ will satisfy
$X=_q Y$ iff $\alpha(X)$ and $\alpha(Y)$ are separated by zero or more
nodes in $\tau$, each of which has a third child that is a
quantifier. All the above propositions about solved forms still hold
if ``dominance'' is systematically replaced with ``qeq''.

>>>>

One aspect in which our definition of \rmrs\ is like dominance
constraints and unlike \mrs\ is that any satisfiable \rmrs\ has an
infinite number of models which only differ in the areas that the
\rmrs\ didn't ``talk about''.  Consider e.g.\ (\ref{ex:cat-erg}).
Read as an \mrs\ or as an \rmrs\ of the previous literature, this
formula is an instruction to build a semantic representation out of
the pieces for ``every fat cat'', ``some dog'', and ``chased''; a
semantic representation as in Fig.~\ref{fig:fat-black-cat} would
\emph{not} be taken as described by this \rmrs.  However, under the
semantics we proposed above, this tree is a correct model of
(\ref{ex:cat-erg}) because all atoms are still satisfied; the \rmrs\
didn't say anything about ``sleep'' or ``run'', but it couldn't
enforce that the tree shouldn't contain those subformulas either.

@@

So far we have based the syntax and semantics of \rmrs\ on the
dominance relation from \newcite{egg:etal:2001} rather than the qeq
relation from \newcite{copestake:etal:2005}.  This is partly because
dominance is a weaker relation than qeq: If a dependency parser links
a determiner to a noun and this noun to a verb, then we can use
dominance but not qeq to represent that the predicate introduced by
the verb is outscoped by the quantifier introduced by the determiner
(see earlier discussion).  However, it is very straightforward to add
qeq to the syntax of the language and to extend the model theory
accordingly.  This extension adds a new atom $X=_q Y$ to
Def.~\ref{defn:rmrs-syntax}, and $\tau,\alpha,g,\sigma$ will satisfy
$X=_q Y$ iff $\alpha(X)$ and $\alpha(Y)$ are separated by zero or more
nodes in $\tau$, each of which has a rightmost child that is a
quantifier. All the above propositions about solved forms still hold
if ``dominance'' is systematically replaced with ``qeq''.
